Supporting Information for "Imperfect slope measurements drive overestimation in standard cone model of lake depth"

### 2021-08-16 figures/00_maps.Rmd
add supp fig showing map of model residuals

>>>>

```{r 00_map_resid, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide', fig.width=6.5}
dt_sf <- st_read("../data/gis.gpkg", "dt", quiet = TRUE) %>%
  mutate(lagoslakeid = as.character(lagoslakeid))
dt   <- readRDS("../data/01_depth_model/depth_grid.rds") %>% # 05_depth_model.R
  mutate(lagoslakeid = as.character(lagoslakeid)) %>%
  mutate(resid = case_when(maxdepth == "maxdepth_true_true" ~ NA_real_,
    TRUE ~ resid)) %>%
  mutate(maxdepth = factor(maxdepth, levels = c(
    "maxdepth_true_true", "maxdepth_true_false",
    "maxdepth_false_true", "maxdepth_false_false"))) %>%
  left_join(dt_sf, by = "lagoslakeid") %>%
  st_as_sf()
dt <- cbind(dt, st_coordinates(dt))

dt <- dt %>% mutate(resid_class =
  smart_cut(resid, c(-20, -10, 0, 10, 20, max(resid)),
    brackets = NULL, sep = " - ")
)

# ----

gg_resid <-
  ggplot() +
  geom_sf(data = st_as_sfc(st_bbox(dt)), alpha = 1, size = 0.6,
    color = "black", fill = "#1D9DCF") +
  geom_sf(data = st_crop(states_all, st_as_sfc(st_bbox(dt))),
    fill = "gray", color = "black", size = 0.3) +
  geom_sf(data = st_crop(states_focal, st_as_sfc(st_bbox(dt))),
    fill = "white", color = "black", size = 0.4) +
  geom_sf(data = dplyr::filter(dt, !is.na(resid)),
    aes(color = resid_class), size = 0.03, alpha = 0.7) +
  labs(color = "Residual") +
  coord_sf(xlim = c(-103.81483, -67.10548), ylim = c(37.5, 48.72102)) +
  theme_void()

gg_resid
```

### 2021-08-16 manuscript/si_template_2019.tex
update title, add reproducibility section to README
add supp fig showing map of model residuals

\title{Supporting Information for "Imperfect slope measurements drive overestimation in geometric models of lake depth"}
%
% e.g., \title{Supporting Information for "Terrestrial ring current:
% Origin, formation, and decay $\alpha\beta\Gamma\Delta$"}
%
%DOI: 10.1002/%insert paper number here%

@@

            \item \textbf{Figure S6:} Characteristics of lakes with bathymetry versus non-bathymetry lakes

            \item \textbf{Figure S7:} Lake characteristics comparison among shape and reservoir classes

            \item \textbf{Figure S8:} Comparison between reported depth and bathymetry depth

@@

\begin{figure}
      \noindent\includegraphics[width=0.85\textwidth]{../figures/01_hypsography-1}
      \caption{Hypsography classification by state. Numbers on panel labels indicate the percentage of lakes in each state with a convex versus a concave cross-section shape.}\label{figS3}
\end{figure}

\begin{figure}
      \noindent\includegraphics[width=0.85\textwidth]{../figures/01_geometry_grid-1}
      \caption{Comparison among lake shape and reservoir classes for A-B) distance to deepest point versus distance to lake visual center and C-D) nearshore slope versus inlake slope. A dashed 1:1 line is shown for comparison. Cross-section shape and reservoir class plots are not identical because not all lakes had a reservoir classification exceeding a 0.75 probability confidence level.}\label{figS4}
\end{figure}

\begin{figure}
      \begin{center}
            \includegraphics[width=0.79\textwidth,keepaspectratio]{../figures/slope_by_area_depth-1}
      \end{center}
      \caption{Comparison between in-lake and nearshore slopes in concave and convex lakes of the same size and max depth. Categories are quantile bins ($<$ 25\%, 25-50\%, 50-75\%, and 75-100\%).}\label{figS5}
\end{figure}
\clearpage

\begin{figure}
      \begin{center}
            \includegraphics[width=\textwidth,keepaspectratio]{../figures/01_slope_compare-1}
      \end{center}
      \caption{Comparison between in-lake and nearshore slope using different calculation techniques. The techniques used in the main text analyses are bolded and the combination of these techniques (top-left corner) produces the strongest relationship between the two metrics. \texttt{slope\_mean} is the mean slope of all inlake or nearshore buffer points. \texttt{slope\_pnts} is the average slope (i.e. \texttt{slope\_pnt}) of all points at maximum depth. \texttt{slope\_online\_mean} is the mean pixel-to-pixel slope of each pixel lying on a straight line either from the single deepest point to the lake shoreline (in the case of inlake slope) or from the lake shoreline point extending to the buffer exterior (in the case of nearshore slope). \texttt{slopes\_online\_mean} is the same as \texttt{slope\_online\_mean} except it uses all inlake points at maximum depth.}\label{figS6}
\end{figure}
\clearpage

>>>>

\title{Supporting Information for "Imperfect slope measurements drive overestimation in standard cone model of lake depth"}
%
% e.g., \title{Supporting Information for "Terrestrial ring current:
% Origin, formation, and decay $\alpha\beta\Gamma\Delta$"}
%
%DOI: 10.1002/%insert paper number here%

@@

            \item \textbf{Figure S6:} Spatial distribution of depth model residuals.

            \item \textbf{Figure S7:} Characteristics of lakes with bathymetry versus non-bathymetry lakes

            \item \textbf{Figure S8:} Lake characteristics comparison among shape and reservoir classes

            \item \textbf{Figure S9:} Comparison between reported depth and bathymetry depth

@@

\begin{figure}
      \noindent\includegraphics[width=0.85\textwidth]{../figures/01_hypsography-1}
      \caption{Hypsography classification by state. Numbers on panel labels indicate the percentage of lakes in each state with a convex versus a concave cross-section shape.}\label{figS2}
\end{figure}

\begin{figure}
      \noindent\includegraphics[width=0.85\textwidth]{../figures/01_geometry_grid-1}
      \caption{Comparison among lake shape and reservoir classes for A-B) distance to deepest point versus distance to lake visual center and C-D) nearshore slope versus inlake slope. A dashed 1:1 line is shown for comparison. Cross-section shape and reservoir class plots are not identical because not all lakes had a reservoir classification exceeding a 0.75 probability confidence level.}\label{figS3}
\end{figure}

\begin{figure}
      \begin{center}
            \includegraphics[width=0.79\textwidth,keepaspectratio]{../figures/slope_by_area_depth-1}
      \end{center}
      \caption{Comparison between in-lake and nearshore slopes in concave and convex lakes of the same size and max depth. Categories are quantile bins ($<$ 25\%, 25-50\%, 50-75\%, and 75-100\%).}\label{figS4}
\end{figure}
\clearpage

\begin{figure}
      \begin{center}
            \includegraphics[width=\textwidth,keepaspectratio]{../figures/01_slope_compare-1}
      \end{center}
      \caption{Comparison between in-lake and nearshore slope using different calculation techniques. The techniques used in the main text analyses are bolded and the combination of these techniques (top-left corner) produces the strongest relationship between the two metrics. \texttt{slope\_mean} is the mean slope of all inlake or nearshore buffer points. \texttt{slope\_pnts} is the average slope (i.e. \texttt{slope\_pnt}) of all points at maximum depth. \texttt{slope\_online\_mean} is the mean pixel-to-pixel slope of each pixel lying on a straight line either from the single deepest point to the lake shoreline (in the case of inlake slope) or from the lake shoreline point extending to the buffer exterior (in the case of nearshore slope). \texttt{slopes\_online\_mean} is the same as \texttt{slope\_online\_mean} except it uses all inlake points at maximum depth.}\label{figS5}
\end{figure}
\clearpage

\begin{figure}
      \begin{center}
            \includegraphics[width=\textwidth,keepaspectratio]{../figures/00_map_resid-1}
      \end{center}
      \caption{Spatial distribution of depth model residuals.}\label{figS6}
\end{figure}
\clearpage
